\begin{prop}
	If SSH holds for a \kfree graph $G$ with $n$ vertices, then $\nu_c(G) \geq \frac{1}{4}n$. 
\end{prop}
\begin{proof}
	Let $\mathcal{M}$ be the collection of branch sets of a $n/2$ SSH-minor of $G$.  Let $\mathcal{M}_1 = \{M\in \mathcal{M}: |M| = 1\}$ and $\mathcal{M}_2 = \{M\in \mathcal{M}: |M| = 2\}$. Then 
\[\nu_c(G) \geq \frac{1}{2}|\mathcal{M}_1| + |\mathcal{M}_2| \geq \frac{1}{2}(|\mathcal{M}_1| + |\mathcal{M}_2|) = \frac{1}{4}n\]
\end{proof}
In Lemma 2.1 of \cite{blas}, Blasiak shows that \kfree graph with connectivity less than $n/2$ satisfies SSH.  We can show the following for higher connectivity.
\begin{lem}
	If $G$ is a \kfree graph on $n$ vertices with $\kappa(G) \geq n/2$, then $\nu_c(G) \geq n-\kappa(G)$.  (Further, if $n/4 < \kappa(G) < n/2$, then $\nu_c(G) \geq \kappa(G)$ and if $\kappa(G) < n/4$ then $\nu_c(G) \geq \frac{1}{4}(n-\kappa(G)$ maybe more) 
\end{lem}
\begin{proof}
	The proof begins similarly to \cite{blas}. Let $S$ be a minimum cut set of $G$.  Then let $L$, $R$ be a partition of $V(G) - S$ so that $L$ and $R$ do not touch.  Since $G$ is \kfree, $L$ and $R$ are cliques, and every vertex of $S$ is complete to $L$ or complete to $R$.  Let $S_L$ be the set of vertices complete to $L$ and $S_R$ the set of vertices complete to $R$.    We claim that between any $A \subseteq S_L$ with $|A| \leq |R|$ and $R$ ($S_R$ and $L$ resp.) there is a matching that saturates $A$.  Suppose there is no $(A, R)$ matching saturating $A$.  Hall's condition then implies that there is $T\subseteq A$ such that $|N(T)\cap R| < |T|$. But then $(S-T)\cup (N(T)\cap R)$ is a cut set separating $L\cup T$ and $R-N(T)$. This set is smaller than $S$, yielding a contradiction.   

Let $M$ be the largest possible matching obtained with $(S_L,R)$ edges and $(S_R,L)$ edges.  This matching is connected, and $|M| = \min\{|S_L|, |R|\} + \min\{|S_R|, |L|\}$.  If both $|R| \leq S_L$ and $|L| \leq S_R$, then we are done.  If, WLOG,  $|R| > S_L$, then let $U_R$ denote the set of vertices of $R$ unmatched by $M$.  Since $|S|\geq n/2$, there are at least $|U_R|$ unmatched vertices of $S_R$ (denoted $U_{S_R}$).  Augment $M$ with any $(U_R , U_{S_R})$ matching saturating $U_R$ to yield $M'$.  These new edges are mutually connected, and connected to any $(S_R,L)$ or $(S_L, R)$ edges via $R$.  Hence, $M'$ is a $(S,S^c)$ connected matching saturating $S^c = R\cup L$, and $|R\cup L| = n-\kappa(G)$. 
\end{proof}



F\"{u}redi et. al note that the stronger version of conjecture \ref{c_conj} is sharp by exhibiting by the $\overline{K_3}$-free graph formed by a disjoint pair of cliques.  In general, if we consider only $\overline{K_3}$-free graphs with sufficiently large cliques it is easy to show that conjecture \ref{c_conj} holds.
\begin{lem}Let $0<c<1/4$.  If $G$ ($\alpha(G) \leq 2$) has $\omega(G) \geq cn$, then $G$ has a $(cn)$-connected matching.
\label{spider}
\end{lem}
\begin{proof}
	Let $S$ be a set of $cn$ vertices inducung a clique.  For any subset of $S'\subseteq S$, the intersection $\displaystyle I = \bigcap_{s\in S'} \{v \in V(G): sv \notin E(G)\}$ induces a clique.  If for any $S'\subseteq S$, $|I| > n/2$, then there is a $cn$-connected matching in the clique induced by $I$.  Otherwise, $|N(S')| \geq |S'|$ for all $S'\subseteq S$, and there is an $S-(V(G)-S)$ matching saturating $S$.  This matching must be connected, since $S$ induces a clique. (This lemma appears implicitly in \cite{FGS})
\end{proof}
This lemma immediately yields several properties that a minimal counterexample to conjecture \ref{c_conj} must possess.
\begin{prop}
 If $G_{c'}$ is a vertex minimal counter example to conjecture \ref{c_conj} with $c = c'$, then the following hold 
\begin{enumerate}
	\item $\omega(G_{c'}) < c'n$
	\item $G_{c'}$ and $\overline{G_{c'}}$ have diameter 2
	\item $G_{c'}$ has no edge dominating $n-c'$ vertices
	\item $\delta(G_{c'}) \geq (1-c')n$.
	\item $G_{c'}$ is $(1-2c')n$-connected.
\end{enumerate}
\end{prop}
