%\RequirePackage[l2tabu, orthodox]{nag}
\RequirePackage{xkvltxp} % needed if passing in a key with space in it
%\documentclass[fancyproof,fontloader=unicode-math,mathfont=XITS Math]{ul-thesis}
%\documentclass[debug,fancyproof,textfont=Linux Libertine O]{ul-thesis}
%\documentclass[final]{ul-thesis}
\documentclass{ul-thesis}

\usepackage{custommacros}
\usetikzlibrary{shapes.misc}

\title{Avoiding, Pretending, and Querying: Three Combinatorial Problems}
\author{Adam S. Jobson}
\degrees{B.S., University of Louisville, 2004\\ M.A., University of Louisville, 2006}
\graduationdate{December 2011}
\defensedate{18 November 2011}
\email{ajobson@gmail.com}
\phone{502-608-1521}
\address{3917 Druid Hills Road}{Louisville, KY 40207}

\usepackage{array}
\newcolumntype{x}[1]{>{\raggedleft\arraybackslash\hspace{0pt}$}p{#1}<{$}}%
\newcolumntype{w}[1]{>{\centering\arraybackslash\hspace{0pt}$}p{#1}<{$}}%

\newcommand*{\mbbRn}[1][n]{\ensuremath{\mathbb{R}^{#1}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\size}{size}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\Row}{Row}
\DeclareMathOperator{\Nul}{Nul}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\Spanop}{Span}
\DeclareMathOperator{\bigO}{O}
\newcommand*{\Span}[1]{\ensuremath{\Spanop\left\{#1\right\}}}
\newcommand*{\adjm}[1]{\ensuremath{A\left(#1\right)}}%
\newcommand*{\indegree}[1]{\ensuremath{d^{-}\left(#1\right)}}
\newcommand*{\outdegree}[1]{\ensuremath{d^{+}\left(#1\right)}}

\usepackage{esvect}
\def\bsrmnxt#1#2{\boldsymbol{\mathrm{#1}}#2}
\newcommand*{\vect}[1]{\ensuremath{\vv{\bsrmnxt#1}}}

\newcommand*{\vectent}[1]{\ensuremath{\boldsymbol{\mathrm{#1}}}}
\newcommand*{\nvect}[1]{\ensuremath{N\vv{\left(#1\right)}}}%


\newcommand*{\zerovect}{\ensuremath{\vv{\text{\bfseries 0}}}}
\newcommand*{\onevect}{\ensuremath{\vv{\text{\bfseries 1}}}}

\newcommand*{\defn}[1]{{\itshape #1}}
\def\AJbf#1{\text{\bfseries{#1}}}%

\newcommand*{\extendbottombound}{\node[vlab,anchor=north] at (current bounding box.south){\vphantom{X}};}
\newcommand*{\extendtopbound}{\node[vlab,anchor=south] at (current bounding box.north){\vphantom{X}};}

\usepackage[section]{placeins}

\addbibresource{Introduction/Introduction.bib}
\addbibresource{QP/QP.bib}
\addbibresource{Adjacency/Adjacency.bib}
\addbibresource{Yao/Yao.bib}
%\addbibresource{Conclusion/Conclusion.bib}

\begin{document}
\frontmatter
\maketitle

\begin{copyrightinfo}%Copyright Page
	Copyright 2011 by Adam S. Jobson

	\ccIconSmall{BY-SA}

	This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit 
\\\url{http://creativecommons.org/licenses/by-sa/3.0/}\\ or send a letter to Creative Commons, 444 Castro Street, Suite 900, Mountain View, California, 94041, USA.
\end{copyrightinfo}

\signaturepage
% optional arguments: [number of blanks][first name][second name]...
% examples \signaturepage[5][Andr\'e K\'ezdy]
%	\signaturepage[5][Andr\'e K\'ezdy][Csaba Biro][Manav Das][Jafar Hadizadeh][Thomas Riedel]

\begin{dedication}
	To my parents.
\end{dedication}

\begin{acknowledgements}
	I wish to thank my advisor, Professor Andr\'e K\'ezdy, for his patience and encouragement. I have learned more from him than I can ever repay.

	To my family, for their unwavering belief in me.

	To Marshall Lagani, Ben Allgeier, Tim Brauch, and Lesley Wellington Wiglesworth, for countless hours of collaboration, both in mathematics and in life.

	To Professors Udayan Darji and Manav Das, for introducing me to higher mathematics and encouraging me to pursue graduate work.

	To Professor Thomas Riedel and everybody in the University of Louisville Department of Mathematics, for their years of support. 

	To Jim Conrey, for introducing me to programming. I cannot imagine where I would be without it.

	To Donald Knuth for creating \TeX, Leslie Lamport for creating \LaTeX, Till Tantau for creating Ti\emph{k}Z, and the thousands of others who have contributed to these projects. Mathematics is even more beautiful thanks to their efforts.
\end{acknowledgements}

\begin{abstract}
	A $k$-term quasi-progression of diameter $d$ is a sequence $\left\{x_1, \ldots, x_k\right\}$ for which there exists a positive integer $l$ such that $l \leq x_{i} - x_{i-1} \leq l+d$, for all $i=2,\ldots,k$. %A quasi-progression with diameter $0$ is simply an arithmetic progression so, in general, 
Quasi-progressions may be thought of as arithmetic progressions with a certain amount of `wiggle-room' allowed. Let $Q\left(d,k\right)$ be the least positive integer such that every $2$-coloring of $\left\{1,\ldots,Q\left(d,k\right)\right\}$ contains a monochromatic $k$-term quasi-progression of diameter $d$.
% Landman [Ramsey Functions for Quasi-Progressions, Graphs and Combinatorics 14 (1998) 131-142] established several results and conjectured that, if $k\geq 2i \geq 1$, then \[ Q_{k-i}\left(k\right) =
%	\begin{cases}
%		2ik-4i+3	&k\not\equiv 1 \pmod{i}\\
%		2ik-2i+1	&k \equiv 1 \pmod{i}
%	\end{cases}\]
We prove a conjecture of Landman for certain values of $k$ and $d$, provide counterexamples for some other cases, and determine that the conjecture always has the correct order of growth.% This is joint work with Andr\'e K\'ezdy, Hunter Snevily, and Susan White.

%\begin{center}\large Pretending: The Row Space of an Adjacency Matrix\end{center}
Let $A$ be the adjacency matrix of a nonempty graph. Is there always a nonzero $\left\{0,1\right\}$-vector in the row space of $A$ that is not a row of $A$? 
%We call such a vector a \emph{hood vector} for the graph, since the vector `looks like' a neighborhood of a vertex in the graph. 
Akbari, Cameron, and Khosrovshahi have shown that an affirmative answer to this question would imply bounds on many graph parameters as a function of the rank of the adjacency matrix. We demonstrate the existence of such vectors for certain families of graphs, examine techniques to find and verify the existence of such vectors, and show that if you generalize the problem to allow asymmetry in the matrices then some $\left\{0,1\right\}$-matrices do not have such vectors.

%\begin{center}\large Querying: Yao's Problem\end{center}
In 1981, Andrew Yao asked ``Should tables be sorted?''. % and provided an answer under some conditions. 
When the table has $n$ cells that are filled with entries taken from a \emph{key space} of $m$ possibilities, he showed that it is possible to decide whether any member of the key space is present in the table by inspecting (querying) only one cell of the table if and only if $m \leq 2n-2$. We make steps toward extending his result to the case where you are permitted two queries by considering several variations of the problem.
\end{abstract}

\tableofcontents*
%\listoftables
%\listoffigures

\mainmatter

%\input{Introduction/Introduction}
\input{Introduction/Glossary}
\input{QP/QP}
\input{Adjacency/Adjacency}
\input{Yao/Yao}
%\input{Conclusion/Conclusion}

\backmatter
\printbibliography
\printglossary
\printindex

\newcommand{\event}[3][]{%
	\begin{minipage}[t]{0.15\textwidth}\scshape #3\end{minipage}
	\begin{minipage}[t]{0.75\textwidth}\textbf{#2}%
		\def\temptyA{#1}%
		\ifx\temptyA\empty\else {\\ \vphantom{.}\hspace{12pt} #1}\fi%
	\end{minipage}\vspace{12pt}
}

\begin{vita}
{\large Education}\vspace{12pt}

\event[Ph.D. in Applied and Industrial Mathematics]{University of Louisville}{2011}

\event[M.S. in Mathematics]{University of Louisville}{2006}

\event[B.S. in Mathematics]{University of Louisville}{2004}

\noindent{\large Publications}\vspace{12pt}

\textit{The Hub Number of a Graph} (with T. Grauman, S. G. Hartke, B. Kinnersley, D. B. West, L. Wiglesworth, P. Worah, H. Wu), \textit{Inform. Process. Lett.} \textbf{108} (2008), 226--228\vspace{12pt}

\textit{On Hamiltonian colorings and hc-stable graphs} (with B. Allgeier, G. Chartrand, L. Nebesk{\'y}, P. Zhang),  \textit{Proceedings of the Thirty-Ninth Southeastern International Conference on Combinatorics, Graph Theory and Computing} (2008) 65--76\vspace{12pt}

\textit{Stack Domination Density} (with T. Brauch, P. Horn, D. J. Wildstrom), submitted.\vspace{12pt}

\textit{Ramsey Functions for Quasi-Progressions with Large Diameter} (with A. K\'ezdy, H. Snevily, S. White), submitted.%\vspace{12pt}
\end{vita}
\end{document}